Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-24 article/article.Rmd
Commit 2024-06-24 06:14

In this study our main focus was to quantify over irradiance events related to CEs. A
key issue for achieving this goal is to  define a threshold for the CE
identification, representative of the clear-sky irradiance at the time of each GHI
measurement. This depends on the selection of the appropriate atmospheric
parameterization for the RTM simulations. The implementation of the long-term change
of AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
of the natural variability of clear-sky GHI. However, the short-term variability of
AOD cannot be taken adequately into account when using monthly values in the model
simulations. We tried different approaches in order to strengthen the robustness of
the methodology and compensate for the limited accuracy of the RTM input data and the
unpredictable natural variability of the atmosphere.

@@

Following the application of the above discussed methodology to the entire dataset 
(`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OIR of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The stronger CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
In the following sections we are discussing the long-term trends and variability of
the CE events as well as of the corresponding OIR and excess irradiation.

>>>>

In this study our main focus was to quantify over irradiance events related to CEs. A
key issue for achieving this goal is to  define a threshold for the CE
identification, representative of the clear-sky irradiance at the time of each GHI
measurement. This depends on the selection of the appropriate atmospheric
parameterization for the RTM simulations. The implementation of the long-term change
of AOD, discussed in section\nobreakspace{}\ref{rtmcs}, allows capturing a large part
of the natural variability of clear-sky GHI. However, the short-term variability of
AOD cannot be taken adequately into account when using monthly values in the model
simulations. We tried different approaches in order to strengthen the robustness of
the methodology and to compensate for the limited accuracy of the RTM input data and
the unpredictable natural variability of the atmosphere.

@@

Following the application of the above discussed methodology to the entire dataset 
(`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 2)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OIR of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The strongest CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
In the following sections we are discussing the long-term trends and variability of
the CE events as well as of the corresponding OIR and excess irradiation.
